---
title: '**VS Results (rDock)**'
author: "Adrià C., Marina M."
header-includes:
   - \usepackage{booktabs}
   - \usepackage{makecell}
output:
  html_document:
    css: https://cdnjs.cloudflare.com/ajax/libs/font-awesome/5.11.2/css/all.css
    self_contained: yes
    theme: yeti
  pdf_document:
    toc: false
    template: default.latex
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(readr)
library(ggplot2)
library(kableExtra)
library(dplyr)
require(knitr)
```

## rDock

This is an R script used to interpret the results from rDock.

```{r, echo=FALSE}


VS_Results_path = '/home/acabello/Documents/NAS/rdock/VS_Results/'
files <- list.files(path = VS_Results_path, pattern = "*.sd", full.names = TRUE)
split_path <- function(x) if (dirname(x)==x) x else c(basename(x),split_path(dirname(x)))
```

## VS_FILTER

--> VS_FILTER.txt

```{bash eval=FALSE}
5
if - -3 SCORE.INTER 1.0 if - SCORE.NRUNS  3 0.0 -1.0,
if - 2 SCORE.RESTR.PHARMA 1.0 if - SCORE.NRUNS  3 0.0 -1.0,
if - -6 SCORE.INTER 1.0 if - SCORE.NRUNS  8 0.0 -1.0,
if - 1 SCORE.RESTR.PHARMA 1.0 if - SCORE.NRUNS 8 0.0 -1.0,
if - SCORE.NRUNS 15 0.0 -1.0,
2
- SCORE.INTER -8,
- SCORE.RESTR.PHARMA 1,

```

--> VS_slurm.q

```{bash eval=FALSE}
#!/bin/bash

#SBATCH -D .
#SBATCH --output=log/rdock_2_filter.q.o
#SBATCH --error=log/rdock_2_filter.q.e
#SBATCH --job-name=rdock_2_filter
#SBATCH --ntasks=1
#SBATCH --cpus-per-task=1
#SBATCH --array=1-700%30

module load rdock
#-------------------------------------------------------------------------
indir=/alexandria1/DB/BigChem_FRAGMENTS/SPLIT_DB/
outdir=VS_Results

num=$(( ${SLURM_ARRAY_TASK_ID} ))
curr_file=`ls $indir*.sd | awk -v line=$num '{if (NR == line) print $0}'`
file_name=`awk 'END{ var=FILENAME; n=split (var,a,/\//); print a[n]}' $curr_file`
#-------------------------------------------------------------------------

rbdock -i $curr_file -o $outdir/docked_filter_2_$file_name -r 4lr6.prm -p dock.prm -t VS_FILTER.txt > 
\$outdir/log/rdock_2_${SLURM_ARRAY_TASK_ID}_filter.log

```



# How many molecules do we have for each file?

```{bash eval=FALSE}
grep -c '$$$$' ./VS_Results/*.sd > howmany.txt
```


```{r eval = FALSE, echo=FALSE}
first50 <- data.frame(matrix(,nrow=700, ncol=2))
colnames(first50) <- c("File_name", "Fragments")

row = 1
for (i in files){
  file <- readLines(i)
  howmany = 0
  for (line in file){
    if (line == "$$$$"){
      howmany = howmany + 1
    }
  }
  #print(split_path(i)[1])
  #print(howmany)
  first50[row, "File_name"] <- split_path(i)[1]
  first50[row, "Fragments"] <- howmany
  row = row + 1
}
```

```{r}

howmany <- read_delim("/home/acabello/Documents/NAS/rdock/howmany.txt", 
    ":", escape_double = FALSE, trim_ws = TRUE,col_names = FALSE)
summary(howmany)
```

```{r}
11122*(700)
sum(howmany$X2)
```


# How many molecules remains after filtering?

--> filter_VS.q

```{r eval=FALSE}
#!/bin/bash

#SBATCH --job-name=test_cluster
#SBATCH -D .
#SBATCH --time=01:00:00
#SBATCH --output=log/test_cluster-%a.q.o
#SBATCH --error=log/test_cluster-%a.q.e
#SBATCH --ntasks=1
#SBATCH --cpus-per-task=1

module load rdock

OUTFILE='FILTERED_SCORE_INTER.sd'

for file in $PWD/VS_Results/*.sd
do
#FILTER DIFERENT MOLECULES
$RBT_ROOT/bin/sdsort -n -fSCORE -s $file |$RBT_ROOT/bin/sdfilter -f'$SCORE.RESTR < 1.0' |$RBT_ROOT/bin/sdfilter -f'$SCORE.INTER < -5.0'
\|$RBT_ROOT/bin/sdfilter -f'$_COUNT == 1'>> tmp.sd
done

#ORDER MOLECULES BY SCORE INTER
$RBT_ROOT/bin/sdsort -n -fSCORE.INTER tmp.sd |$RBT_ROOT/bin/sdfilter -f'$_COUNT == 1' >> $OUTFILE

#echo Compressing \${sdout}...
#rm tmp.sd
#gzip -9vf \${sdout}

```


```{bash eval=FALSE}
grep -c '$$$$' ./NAS/acabello/rdock/FILTERED_SCORE_INTER.sd
```

418.321 molecules.


# Distribution of the intermolecular scores.

```{r, echo=FALSE}
INTERMOLECULAR <- read_table2("/home/acabello/Documents/NAS/rdock/700_sortedINTER.rep")
summary(INTERMOLECULAR)
inter<-ggplot(data=INTERMOLECULAR, aes(x=INTER))+
  geom_histogram(aes(label=..count.., fill=(..count..)/sum(..count..)), binwidth=1)+scale_fill_continuous(type = "viridis")+
    stat_bin(binwidth=1, geom="text", size=2,
           aes(label=..count..), vjust= -0.8)+xlim(-20,-2)+
  ylab("Counts")+
  theme_classic()+ ggtitle("INTER SCORES")
inter

norm_INTER <- read_table2("/home/acabello/Documents/NAS/rdock/700_INTERnorm.rep")

pnorminter<-ggplot(data=norm_INTER, aes(x=SCORE.INTER.norm))+
  geom_histogram(aes(label=..count.., fill=(..count..)/sum(..count..)), binwidth=0.1)+scale_fill_continuous(type = "viridis")+
    stat_bin(binwidth=0.1, geom="text", size=2.5,
           aes(label=..count..), vjust= -0.6)+
  ylab("Counts")+
  theme_classic()+ ggtitle("NORM INTER SCORES")
pnorminter

```

```{r, echo=FALSE}
restr<-ggplot(data=INTERMOLECULAR, aes(x=RESTR))+
  geom_histogram(aes(label=..count.., fill=(..count..)/sum(..count..)), binwidth=0.1)+scale_fill_continuous(type = "viridis")+
    stat_bin(binwidth=0.1, geom="text", size=2,
           aes(label=..count..), vjust= -0.8)+
  ylab("Counts")+
  theme_classic()+ ggtitle("RESTR SCORES")
restr
```

```{r}
library(dplyr)
FILTER <- filter(INTERMOLECULAR, INTER <= -12 & RESTR <= 0.7)
dim(FILTER)
```
```{r}
(dim(FILTER)[1]/700)*5800
```

Molecules that will be used for clustering.

\clearpage
\newpage

## Using Score.Inter -12 and Score.Restr 0.7

```{r, echo=FALSE}
INTERMOLECULAR1207 <- read_table2("/home/acabello/Documents/NAS/rdock/FILTERED_1207.rep")

restr<-ggplot(data=INTERMOLECULAR1207, aes(x=RESTR))+
  geom_histogram(aes(label=..count.., fill=(..count..)/sum(..count..)), binwidth=0.1)+scale_fill_continuous(type = "viridis")+
    stat_bin(binwidth=0.1, geom="text", size=2,
           aes(label=..count..), vjust= -0.8)+
  ylab("Counts")+
  theme_classic()+ ggtitle("RESTR SCORES")
restr

inter<-ggplot(data=INTERMOLECULAR1207, aes(x=INTER))+
  geom_histogram(aes(label=..count.., fill=(..count..)/sum(..count..)), binwidth=1)+scale_fill_continuous(type = "viridis")+
    stat_bin(binwidth=1, geom="text", size=2,
           aes(label=..count..), vjust= -0.8)+
  ylab("Counts")+
  theme_classic()+ ggtitle("INTER SCORES")
inter

norm_INTER <- read_table2("/home/acabello/Documents/NAS/rdock/FILTERED_1207_norm.rep")

pnorminter<-ggplot(data=norm_INTER, aes(x=SCORE.INTER.norm))+
  geom_histogram(aes(label=..count.., fill=(..count..)/sum(..count..)), binwidth=0.1)+scale_fill_continuous(type = "viridis")+
    stat_bin(binwidth=0.1, geom="text", size=2.5,
           aes(label=..count..), vjust= -0.6)+
  ylab("Counts")+
  theme_classic()+ ggtitle("NORM INTER SCORES")
pnorminter
```



# Comparision Database, ChEMBL, and PDB


```{r, echo=FALSE}
Unique_Fragments <- 4123967

ChemBL <- read_table2("/home/acabello/Desktop/Unique_ChEMBL_report.tbl")
PDB <- read_table2("/home/acabello/Desktop/HB_dock_unique_report.tbl")

summary(PDB)
interCHEMBL<-ggplot(data=ChemBL, aes(x=INTER))+
  geom_histogram(aes(label=..count.., fill=(..count..)/sum(..count..)), binwidth=1)+scale_fill_continuous(type = "viridis")+
    stat_bin(binwidth=1, geom="text", size=2,
           aes(label=..count..), vjust= -0.8)+xlim(-20,-2)+
  ylab("Counts")+
  theme_classic()+ ggtitle("INTER SCORES ChEMBL")
interCHEMBL
interPDB<-ggplot(data=PDB, aes(x=INTER))+
  geom_histogram(aes(label=..count.., fill=(..count..)/sum(..count..)), binwidth=1)+scale_fill_continuous(type = "viridis")+
    stat_bin(binwidth=1, geom="text", size=2,
           aes(label=..count..), vjust= -0.8)+xlim(-21,-2)+
  ylab("Counts")+
  theme_classic()+ ggtitle("INTER SCORES PDB")
interPDB
summary(ChemBL)
```
```{r}
interCHEMBL
interPDB<-ggplot(data=ChemBL, aes(x=RESTR))+
  geom_histogram(aes(label=..count.., fill=(..count..)/sum(..count..)), binwidth=1)+scale_fill_continuous(type = "viridis")+
    stat_bin(binwidth=1, geom="text", size=2,
           aes(label=..count..), vjust= -0.8)+
  ylab("Counts")+
  theme_classic()+ ggtitle("RESTR SCORES ChEMBL")
interPDB
summary(ChemBL)
```


```{r}
per20ChemBLG <- ChemBL %>%
  filter(INTER < -20)

per20ChemBL <- ChemBL %>%
  filter(INTER >= -20,
         INTER < -18)

per18ChemBL <- ChemBL %>%
  filter(INTER >= -18,
         INTER < -16)

per16ChemBL <- ChemBL %>%
  filter(INTER >= -16,
         INTER < -14)

per14ChemBL <- ChemBL %>%
  filter(INTER >= -14,
         INTER < -12)


per12ChemBL <- ChemBL %>%
  filter(INTER >= -12,
         INTER < -10)


per10ChemBL <- ChemBL %>%
  filter(INTER >= -10,
         INTER < -8)


per8ChemBL <- ChemBL %>%
  filter(INTER >= -8)


per20PDBG <- PDB %>%
  filter(INTER < -20)

per20PDB <- PDB %>%
  filter(INTER >= -20,
         INTER < -18)

per18PDB <- PDB %>%
  filter(INTER >= -18,
         INTER < -16)

per16PDB <- PDB %>%
  filter(INTER >= -16,
         INTER < -14)

per14PDB <- PDB %>%
  filter(INTER >= -14,
         INTER < -12)

per12PDB <- PDB %>%
  filter(INTER >= -12,
         INTER < -10)

per10PDB <- PDB %>%
  filter(INTER >= -10,
         INTER < -8)

per8PDB <- PDB %>%
  filter(INTER >= -8)


per20G <- INTERMOLECULAR %>%
  filter(INTER < -20)

per20 <- INTERMOLECULAR %>%
  filter(INTER >= -20,
         INTER < -18)

per18 <- INTERMOLECULAR %>%
  filter(INTER >= -18,
         INTER < -16)

per16 <- INTERMOLECULAR %>%
  filter(INTER >= -16,
         INTER < -14)

per14 <- INTERMOLECULAR %>%
  filter(INTER >= -14,
         INTER < -12)

per12 <- INTERMOLECULAR %>%
  filter(INTER >= -12,
         INTER < -10)

per10 <- INTERMOLECULAR %>%
  filter(INTER >= -10,
         INTER < -8)

per8 <- INTERMOLECULAR %>%
  filter(INTER >= -8)

```

\clearpage
\newpage


```{r}
cumPer <- c(dim(per20G)[1], dim(per20)[1],dim(per18)[1],dim(per16)[1],dim(per14)[1],dim(per12)[1],dim(per10)[1],dim(per8)[1],(Unique_Fragments-dim(INTERMOLECULAR)[1]))
cumPerChEMBL <- c(dim(per20ChemBLG)[1], dim(per20ChemBL)[1],dim(per18ChemBL)[1],dim(per16ChemBL)[1],dim(per14ChemBL)[1],dim(per12ChemBL)[1],dim(per10ChemBL)[1],dim(per8ChemBL)[1],0)
cumPerPDB <- c(dim(per20PDBG)[1], dim(per20PDB)[1],dim(per18PDB)[1],dim(per16PDB)[1],dim(per14PDB)[1],dim(per12PDB)[1],dim(per10PDB)[1],dim(per8PDB)[1],0)



text_tbl <- data.frame(cutoff = c("< -20","[-20,-18)","[-18,-16)","[-16,-14)","[-14,-12)","[-12,-10)","[-10,-8)", ">= -8", "Filtered (HTVS)"),
  chem = round((100*cumsum(cumPerChEMBL)/sum(cumPerChEMBL)),1),
  pdbb = round((100*cumsum(cumPerPDB)/sum(cumPerPDB)),1),
  database = round((100*cumsum(cumPer)/sum(cumPer)),1)
)

text_tbl %>%
  mutate_all(linebreak) %>%
  kable(col.names = linebreak(c("Cutoff (Score.Inter)","% Actives (ChEMBL)","% Actives (PDB)","% Database")))%>%
  kable_classic(full_width = F, html_font = "Cambria")

```


```{r}
per20G1 <- INTERMOLECULAR1207 %>%
  filter(INTER < -20)

per201 <- INTERMOLECULAR1207 %>%
  filter(INTER >= -20,
         INTER < -18)

per181 <- INTERMOLECULAR1207 %>%
  filter(INTER >= -18,
         INTER < -16)

per161 <- INTERMOLECULAR1207 %>%
  filter(INTER >= -16,
         INTER < -14)

per141 <- INTERMOLECULAR1207 %>%
  filter(INTER >= -14,
         INTER < -12)

per121 <- INTERMOLECULAR1207 %>%
  filter(INTER >= -12,
         INTER < -10)

per101 <- INTERMOLECULAR1207 %>%
  filter(INTER >= -10,
         INTER < -8)

per81 <- INTERMOLECULAR1207 %>%
  filter(INTER >= -8)

cumPer2 <- c(dim(per20G1)[1], dim(per201)[1],dim(per181)[1],dim(per161)[1],dim(per141)[1],dim(per121)[1],dim(per101)[1],dim(per81)[1], 
             (Unique_Fragments-dim(INTERMOLECULAR1207)[1]))

cumPerChEMBL <- c(dim(per20ChemBLG)[1], dim(per20ChemBL)[1],dim(per18ChemBL)[1],dim(per16ChemBL)[1],dim(per14ChemBL)[1],dim(per12ChemBL)[1],dim(per10ChemBL)[1],dim(per8ChemBL)[1],
                  0)

cumPerPDB <- c(dim(per20PDBG)[1], dim(per20PDB)[1],dim(per18PDB)[1],dim(per16PDB)[1],dim(per14PDB)[1],dim(per12PDB)[1],dim(per10PDB)[1],dim(per8PDB)[1],
               0)



text_tbl <- data.frame(cutoff = c("< -20","[-20,-18)","[-18,-16)","[-16,-14)","[-14,-12)","[-12,-10)","[-10,-8)", ">= -8", "Filtered (HTVS)"),
  chem = round((100*cumsum(cumPerChEMBL)/sum(cumPerChEMBL)),1),
  pdbb = round((100*cumsum(cumPerPDB)/sum(cumPerPDB)),1),
  database = round((100*cumsum(cumPer2)/sum(cumPer2)),1)
)

text_tbl %>%
  mutate_all(linebreak) %>%
  kable(col.names = linebreak(c("Cutoff (Score.Inter)","% Actives (ChEMBL)","% Actives (PDB)","% Database")))%>%
  kable_classic(full_width = F, html_font = "Cambria")
```




# FINAL RESULTS VS

```{bash eval=FALSE}
grep -c '$$$$' FILTERED_SCORE_INTER_12.sd
```

1.542.571 molecules.

## Score distribution

```{r}
INTERMOLECULAR_FINAL <- read_table2("/home/acabello/Desktop/FILTERED_SCORE_INTER_12_REPORT.tbl")
dim(INTERMOLECULAR_FINAL)
summary(INTERMOLECULAR_FINAL)
```


```{r}
restrF<-ggplot(data=INTERMOLECULAR_FINAL, aes(x=RESTR))+
  geom_histogram(aes(label=..count.., fill=(..count..)/sum(..count..)), binwidth=0.1)+scale_fill_continuous(type = "viridis")+
    stat_bin(binwidth=0.1, geom="text", size=2,
           aes(label=..count..), vjust= -0.8)+
  ylab("Counts")+
  theme_classic()+ ggtitle("RESTR SCORES")
restrF

interF<-ggplot(data=INTERMOLECULAR_FINAL, aes(x=INTER))+
  geom_histogram(aes(label=..count.., fill=(..count..)/sum(..count..)), binwidth=1)+scale_fill_continuous(type = "viridis")+
    stat_bin(binwidth=1, geom="text", size=2,
           aes(label=..count..), vjust= -0.8)+xlim(-20,-2)+
  ylab("Counts")+
  theme_classic()+ ggtitle("INTER SCORES")
interF

```

## Summary table
```{r}
CHEMBL1163125[CHEMBL1163125$`Molecule ChEMBL ID` == "CHEMBL112",]
#summary(INTERMOLECULAR_FINAL)
```

```{r}
per20GF <- INTERMOLECULAR_FINAL %>%
  filter(INTER < -20)

per20F <- INTERMOLECULAR_FINAL %>%
  filter(INTER >= -20,
         INTER < -18)

per18F <- INTERMOLECULAR_FINAL %>%
  filter(INTER >= -18,
         INTER < -16)

per16F <- INTERMOLECULAR_FINAL %>%
  filter(INTER >= -16,
         INTER < -14)import os
from rdkit import RDConfig

per14F <- INTERMOLECULAR_FINAL %>%
  filter(INTER >= -14,
         INTER < -12)

per12F <- INTERMOLECULAR_FINAL %>%
  filter(INTER >= -12,
         INTER < -10)

per10F <- INTERMOLECULAR_FINAL %>%
  filter(INTER >= -10,
         INTER < -8)

per8F <- INTERMOLECULAR_FINAL %>%
  filter(INTER >= -8)

cumPerF <- c(dim(per20GF)[1], dim(per20F)[1],dim(per18F)[1],dim(per16F)[1],dim(per14F)[1],dim(per12F)[1],dim(per10F)[1],dim(per8F)[1], 
             (Unique_Fragments-dim(INTERMOLECULAR_FINAL)[1]) )


cumPerChEMBL <- c(dim(per20ChemBLG)[1], dim(per20ChemBL)[1],dim(per18ChemBL)[1],dim(per16ChemBL)[1],dim(per14ChemBL)[1],dim(per12ChemBL)[1],dim(per10ChemBL)[1],dim(per8ChemBL)[1],
                  0)

cumPerPDB <- c(dim(per20PDBG)[1], dim(per20PDB)[1],dim(per18PDB)[1],dim(per16PDB)[1],dim(per14PDB)[1],dim(per12PDB)[1],dim(per10PDB)[1],dim(per8PDB)[1],
               0)
dim(per14F)[1]/(Unique_Fragments-dim(INTERMOLECULAR_FINAL)[1])


text_tbl <- data.frame(cutoff = c("< -20","[-20,-18)","[-18,-16)","[-16,-14)","[-14,-12)","[-12,-10)","[-10,-8)", ">= -8", "Filtered (HTVS)"),
  chem = round((100*cumsum(cumPerChEMBL)/sum(cumPerChEMBL)),1),
  pdbb = round((100*cumsum(cumPerPDB)/sum(cumPerPDB)),1),
  database = round((100*cumsum(cumPerF)/sum(cumPerF)),1)
)

text_tbl %>%
  mutate_all(linebreak) %>%
  kable(col.names = linebreak(c("Cutoff (Score.Inter)","% Actives (ChEMBL)","% Actives (PDB)","% Database")))%>%
  kable_classic(full_width = F, html_font = "Cambria")
```
```{r}

print(paste("There are",dim(INTERMOLECULAR_FINAL)[1], "molecules as a final result of rDock."))
print(paste("rDock has filtered",(Unique_Fragments-dim(INTERMOLECULAR_FINAL)[1]),"molecules."))
print(paste("The sum of the filtered", (Unique_Fragments-dim(INTERMOLECULAR_FINAL)[1]), "and the results from rDock",dim(INTERMOLECULAR_FINAL)[1],"is  ",(Unique_Fragments-dim(INTERMOLECULAR_FINAL)[1])+(dim(INTERMOLECULAR_FINAL)[1])))
print(paste("The SUM of each one of the intervals used in the table is",sum(c(dim(per20GF)[1], dim(per20F)[1],dim(per18F)[1],dim(per16F)[1],dim(per14F)[1],dim(per12F)[1],dim(per10F)[1],dim(per8F)[1]))))
print(paste("If we sum the result to the ones that have not been screened", sum(c(dim(per20GF)[1], dim(per20F)[1],dim(per18F)[1],dim(per16F)[1],dim(per14F)[1],dim(per12F)[1],dim(per10F)[1],dim(per8F)[1])) + (Unique_Fragments-dim(INTERMOLECULAR_FINAL)[1])))

dim(per20GF)[1]/Unique_Fragments
dim(per20GF)[1]/dim(INTERMOLECULAR_FINAL)[1]
100-((Unique_Fragments-dim(INTERMOLECULAR_FINAL)[1])*100/Unique_Fragments)
```

```{r}
prova <- c(dim(per20GF)[1], dim(per20F)[1],dim(per18F)[1],dim(per16F)[1],dim(per14F)[1],dim(per12F)[1],dim(per10F)[1],dim(per8F)[1])
sum(prova)/Unique_Fragments
```

